Measuring contrast processing in the visual system using SSVEP (and VEP?)

### 2024-04-02 review.qmd
Adding DeVries

This general approach has revealed much about the development of visual abilities in infants [@braddick, @atkinson]. In general, SSVEP measurements of infant vision have revealed that contrast sensitivity for both achromatic and chromatic contrast as well as stereoscopic depth perception develops earlier than had been supposed previously based on behavioural readouts [@dobsonVisualAcuityHuman1978; @norciaSpatialFrequencySweep1985, ] with both chromatic and achromatic contrast detection reaching near-adult levels by around six months while spatial acuity as measured by SSVEP reaches adult levels more slowly but near-adult levels are recorded around 1 year [[@NorciaTyler1985, @HamerVisRed1989]] compared to  around 6-7 years with behavioural measures [@Ellemberg vis res 1999, @Atkinson]. At least some of this difference is likely due to the relatively objectivity and high SNR of the SSVEP technique compared to other methods such as preferential looking which require careful measurement of the infant's gaze direction. 
The SSVEP technique has also been used to study the development of the contrast gain control mechanisms described in the previous section.[@Candy 2001, @PeiNorcia 2017]. Although contrast gain control is measurable in infants as young as six weeks old (@Candy2001, @MorroneBurr1986, @Skoczenski & Norcia, 1998), development appears to be slower with adult levels being reached in approximately 11 years. [@PeiNorcia].

>>>>

This general approach has revealed much about the development of visual abilities in infants [@braddick, @atkinson]. In general, SSVEP measurements of infant vision have revealed that contrast sensitivity for both achromatic and chromatic contrast as well as stereoscopic depth perception develops earlier than had been supposed previously based on behavioural readouts [@dobsonVisualAcuityHuman1978; @norciaSpatialFrequencySweep1985, ] with both chromatic and achromatic contrast detection reaching near-adult levels by around six months while spatial acuity as measured by SSVEP reaches adult levels more slowly but near-adult levels are recorded around 1 year [@NorciaTyler1985, @HamerVisRed1989] compared to  around 6-7 years with behavioural measures [@Ellemberg vis res 1999, @Atkinson]. At least some of this difference is likely due to the relatively objectivity and high SNR of the SSVEP technique compared to other methods such as preferential looking which require careful measurement of the infant's gaze direction although it should be noted that other groups have reported electrophysiological correlates of visual acuity that more closely match the behavioural measures [@de1982maturation].

The SSVEP technique has also been used to study the development of the contrast gain control mechanisms described in the previous section.[@Candy 2001, @PeiNorcia 2017]. Although contrast gain control is measurable in infants as young as six weeks old (@Candy2001, @MorroneBurr1986, @Skoczenski & Norcia, 1998), development appears to be slower with adult levels being reached in approximately 11 years. [@PeiNorcia].
